### 2013-12-03 inst/doc/manuscript.Rmd
tweak documentation, metadata tests
renamed tree access methods get_trees and get_trees_list, in closer analogy to get_characters and _get_characters_list.  The first provides a smart/integrated representation, whereas the latter provides a consistent but more cumbersome structure that corresponds 1:1 with the NeXML heirarchy

The resulting `nex` object is an R

>>>>

The resulting `nex` object is an R object representation of the NeXML.

```{r}
phy <- get_trees(nex)
plot(phy)
```

Where we have used the standard plotting function from the `ape` package to plot the resulting `ape::phylo` object returned by `get_trees`.

NeXML can not only contain multiple phylogenetic trees in a single file, but can also group sets of trees into separate blocks.  The `get_trees` function attempts to return the most sensible R object for NeXML: if only a single tree is available, it will return an `ape::phylo` object; if multiple trees are available in a single `trees` block, it will return an `ape::multiPhylo` object (a list of `phylo` objects).  If multiple blocks are available, it will return a list of `multiPhylo` blocks.  While most users will find this behavior convenient, there are times (such as looping over many NeXML files) when having a variable return type is undisirable.  To always get back a list of `multiPhylo` objects, even when only one tree is available, use `get_trees_list()`.

##### Character data
